### 2025-04-15 Thesis/Latex/Acknowledgements.tex

\chapter*{Acknowledgements}
\thispagestyle{empty}
%\addcontentsline{toc}{chapter}{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\chapter*{Acknowledgements}
\thispagestyle{empty}
%\addcontentsline{toc}{chapter}{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}

	First of all, praise and thanks to Allah Almighty for giving us all the patience, courage, will and motivation that allowed us to accomplish this work.\\ 
	\vspace{0.3cm}

	My deepest gratitude goes to my supervisor, \textbf{Mr Salem Mohamed } for his patient guidance, insightful feedback, and continuous encouragement throughout the course of this work .\\
	\vspace{0.3cm}
	I would like to acknowledge the members of the jury for their interest  \\
	\vspace{0.3cm}
    I am also especially thankful to my parents, family, and friends for their unwavering support, love, and motivation at every step of this journey. \\
    \vspace{0.3cm}
    I would like to thank everyone who helps me to improve my work. and who gave me any remark that helped me to perfect this manuscript.\\
	\vspace{0.3cm}
	All the teachers of the University MUSTAPHA STAMBOULI DE LA WILAYA MASCARA For the good contribution of this work.
\end{center}

### 2025-04-15 Thesis/Latex/Chapter_4.tex

\chapter{k Selection in Retrieval}
\section{Introduction}
Retrieval-Augmented Generation (RAG) systems enhance language models by grounding responses in externally retrieved documents.A critical challenge in these systems is determining the optimal number of documents (k) to retrieve for a given query.Current approaches fall into three categories: static k selection, which uses a fixed number of retrieved documents; dynamic k selection, which adjusts k based on query  characteristics; and hybrid approaches, which combine both strategies.In this chapter, we first explore methods, highlighting their strengths and limitations We then introduce our novel hybrid dynamic selection algorithm provide detailed description of its methodology and present experimental results that demonstrate the effectiveness of its performance . 
%\section {The Role of k in Retrieval-Augmented Generation}
%The number of retrieved documents (k) is a critical parameter in Retrieval-Augmented Generation (RAG) that has a direct impact on the retrieval and generation phases. Choosing the right k ensures that the system retrieves enough relevant information. 
\section{Defining k: The Number of Retrieved Documents}
the parameter k denotes the number of documents or passages retrieved from an external knowledge base. This retrieval process is managed by the retriever component\cite{pareto2024rag},which identifies the top k relevant documents based on similarity to the query typically using embedding-based search\cite{Rossi_2024} (e.g., dense retrieval with FAISS, BM25, or hybrid methods) Subsequently, these documents are passed to the generator, typically a language model, which synthesizes the final response by integrating the retrieved 
\begin{figure}[h]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/topk.png}
	\caption{Basic retrieval}
	\label{rag_retrival.png}

\end{figure}
\newline
\section{Impact of k on Retrieval Performance}
The retriever's effectiveness in identifying relevant documents depends on k. Key impacts include :
\subsection{Recall vs. Precision} 
When a user conducts a search query, the outcomes from the database can be grouped into four distinct types based on relevance and retrieval status \cite{geeksforgeeks2022precision}:
\begin{itemize}
	\item {Relevant and Retrieved:} Documents that both address the user’s query and appear in the search results.
	\item {Relevant and Not Retrieved:} Useful documents that answer the query but are not included in the results.

	\item {Non-Relevant and Retrieved:} Documents that appear in the results but lack meaningful value for the query.

	\item {Non-Relevant and Not Retrieved:} Irrelevant documents excluded from the results.
\end{itemize}

\textbf{Precision@k}: evaluates the proportion of relevant documents within the top k retrieved results. This metric is particularly valuable in scenarios where the focus is on delivering highly relevant information quickly, rather than ensuring complete coverage such as ,recommendation systems or search engines\cite{deconvoluteai2024metrics}.

\[
\text{Precision@k} = \frac{\text{Number of Relevant Items Retrieved in Top k}}{k}
\]

\textbf{Example}
Suppose we have a dataset of 10 documents. If we retrieve \( k = 4 \) documents and find that 3 of them are relevant to the query:

\begin{itemize}
	\item \textbf{Dataset}: [doc1, doc2, doc3, doc4, doc5, doc6, doc7, doc8, doc9, doc10]
	\item \textbf{Retrieved}: [doc3, doc1, doc7, doc4]
	\item \textbf{Relevant}: [doc1, doc3, doc5, doc8]
\end{itemize}

The Precision@4 score would be:

\[
\text{Precision@4} = \frac{3}{4} = 0.75
\]

\textbf{Recall@k :}evaluates the proportion of relevant documents that are successfully retrieved within the top k results. This metric is particularly important in contexts where ensuring the completeness of information is crucial, such as in medical research or academic tools, where omitting relevant documents could result in incomplete or inaccurate conclusions\cite{deconvoluteai2024metrics}.

\[
\text{Recall@k} = \frac{\text{Number of Relevant Items Retrieved in Top k}}{\text{Total Number of Relevant Items}}
\]
\newline
\textbf{Example}
Consider a dataset of 10 documents. If we retrieve \( k = 4 \) documents and find that 2 of them are relevant, while the total number of relevant documents in the dataset is 4:

\[
\text{Recall@4} = \frac{2}{4} = 0.5
\]

Increasing k typically enhances recall by retrieving more relevant documents but may decrease precision due to the inclusion of irrelevant ones. Conversely, decreasing k can improve precision but at the cost of lower recall. 
\subsection{Retrieval Speed and Computational Cost}
Retrieval speed and computational cost are two important areas where k has a big influence Below is a detailed explanation of how higher k values affect these aspects.

\textbf{Increased Computational Resources:} \\
As the value of k expands, the retrieval system must handle a larger set of documents, leading to higher computational demands. Specifically, the system needs to perform additional operations like ranking, filtering, and similarity scoring to identify the most relevant documents. These tasks become increasingly resource-intensive, particularly in large-scale retrieval settings where the document corpus consists of millions or even billions of entries\cite{manning2008ir}. For instance, retrieving the top  documents (k=80) requires significantly more computational resources compared to retrieving only the top 10 documents (k=5).

\textbf{Higher Memory Usage:}
As the number of retrieved documents (k) increases ,Storing and processing a larger set of retrieved documents requires more memory This can become a significant bottleneck, especially in environments with constrained memory resources .

For large-scale retrieval tasks, where datasets may contain millions or even billions of documents, the memory demand grows proportionally with 
k. Each retrieved document needs to be stored temporarily, along with its associated metadata, such as embedding vectors, BM25 scores, or other relevance signals. Additionally, sorting and filtering operations further contribute to memory overhead
\subsection{Document Ranking Quality}
Document ranking in information retrieval involves ordering documents by their relevance to a user's query. The objective is to prioritize the most relevant documents at the top of search results, making it easier for users to access useful information quickly. Different models,Vector Space, including Boolean, and Probabilistic models, are used to establish this ranking \cite{enwiki:1262179867}.\\

Increasing the number of retrieved documents,represented as k, may result in the addition of lower-ranked, less relevant documents, potentially diluting the overall quality of the retrieved information. This occurs because of the inherent balance between precision and recall in information retrieval systems.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{Figures/precisionR.png}
	\caption{Precision in Document Ranking\cite{evidentlyai2025}}
	\label{precisionR}

\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{Figures/recalR.png}
	\caption{Recall in Document Ranking\cite{evidentlyai2025}}
	\label{recalR}

\end{figure}
As k grows, recall generally improves since a larger number of relevant documents are likely to be retrieved as shown in Figure \ref{recalR}. However, this often comes at the expense of precision, as the additional documents retrieved may include non-relevant ones,thereby lowering the overall precision as illustrated in Figure \ref{precisionR}. This trade-off is a core principle in evaluating information retrieval systems.

\section{Impact of k on Generation Quality}
The impact of k (the number of retrieved documents or generated candidates) on generation quality is A crucial factor in many machine learning and information retrieval tasks, including text generation, recommendation systems, and search engines .

\subsection{Trade-off Between Diversity and Relevance} 
Higher k: Increasing k often improves diversity in generated outputs or retrieved documents, as more candidates are considered. However, this can lead to a drop in relevance or quality, as lower-ranked candidates may be less accurate or coherent. \\
Lower k: A smaller k tends to prioritize high-quality, relevant outputs but may lack diversity, leading to repetitive or overly narrow results.

Research shows that the quality of retrieved documents plays a crucial role in the performance of Retrieval-Augmented Generation (RAG) systems. For example, one study demonstrated that the precision of retrieved documents directly affects the factual correctness of the generated responses \cite{salemi2023evaluating}
Additionally, another study revealed that simply increasing the number of documents does not necessarily improve generation quality,especially if the additional documents are not highly relevant\cite{wan2025cognitivealigneddocumentselectionretrievalaugmented}
\subsection {Effect on Text Generation Models}
In text generation tasks, such as machine translation and dialogue systems, The parameter k frequently refers to the beam width in beam search algorithms\cite{freitag-al-onaizan-2017-beam}. Beam search is a heuristic search algorithm that expands the most promising nodes in a graph to maximize the quality of the text that is produced. Adjusting the beam width (k) has significantly impacts how well text generation models function.

As the beam width is increased, the model must process and retain more candidate sequences concurrently, leading to higher computational and memory demands Particularly in real-time applications where latency is crucial, this increase may have an effect on system performance and response time\cite{tensorrt_llm_beam_search}.

\section{Existing Solutions for k Selection}
Selecting an optimalnk plays a crucial role in balancing retrieval effectiveness and generation quality.Over the years, various strategies have been proposed to determine k, ranging from static selection to dynamic and hybrid approaches.
\subsection{Static k Selection}
\subsection{Dynamic k Selection}
\subsection{Hybrid k Selection}
\section{ Proposed Solution}
\subsection{Mixture of Logits-Based k Selection}
\subsection{Algorithm Design}
\subsection{Pseudocode}
\section{ Conclusion }

>>>>

\chapter{Experimental Results}
\pagestyle{fancy}\lhead{\textbf \footnotesize\it{Experimental Results}}
\pagestyle{fancy}\chead{} \pagestyle{fancy}\rhead{}
\pagestyle{fancy}\lfoot{\textbf {\small\it{Univ-Mascara/Computer Science: 2025}}} 
\pagestyle{fancy}\cfoot{} \pagestyle{fancy}\rfoot{\thepage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{start6}
In this chapter, we present the experimental results of applying our novel algorithm to SASRec and compare its performance with SASRec tested using MOL. The goal of these experiments is to assess the effectiveness of our approach in improving recommendation accuracy, model efficiency, and overall performance metrics.

\section{Experimental Results}\label{sec3}
In order to measure the effectiveness of our proposed method, we perform a comprehensive evaluation of both the retrieval algorithm and the Mixture-of-Logits (MoL) approach. This assessment focuses on the next-item prediction task, a fundamental challenge in recommendation systems\cite{kang2018selfat},
where the goal is to predict the most relevant item a user will interact with next based on their past interactions. 
\subsection{Dataset}
We conducted experiments using two MovieLens datasets : ML-100K and ML-1M \cite{Harper2015}which are widely used benchmarks for evaluating sequential recommendation models as detailed in Table\ref{tab_movielens}.\\
\begin{table}[h]
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{tabular}{|l|p{10cm}|}
		\hline
		\textbf{Dataset} & \textbf{Description} \\
		\hline
		\textbf{MovieLens-100K} & 100,000 ratings (1-5 scale) from 943 users on 1,682 movies. \\
		& Each user has rated at least 20 movies. \\
		& Includes user demographic information (age, gender, occupation, zip code). \\
		\hline
		\textbf{MovieLens-1M} & 1,000,209 ratings from 6,040 users on approximately 3,900 movies. \\
		& Data collected from users who joined MovieLens in 2000. \\
		& Represents a larger-scale recommendation scenario. \\
		\hline
	\end{tabular}
	\caption{Summary of MovieLens datasets}
	\label{tab_movielens}
\end{table}

\subsection{ Setup }For both datasets, We utilize the SASRec architecture as our sequential user encoder, a model renowned for achieving state-of-the-art performance in next-item prediction tasks. This architecture processes the user's historical interaction sequence, generating embeddings that encapsulate the user's preferences at each time step. These embeddings serve as the foundation for predicting the next item in the sequence.

The query \( q \) represents the user's state at a specific time step, derived from their interaction history. In the MoL (Mixture of Logits) framework,\( q \)is transformed into \( Pq \)
embeddings through a multi-layer perceptron (MLP).
\subsection{Impact of Hyperparameters}
For fair comparison, we maintained consistent architectural choices and training conditions across all experiments, We conducted an extensive hyperparameter analysis comparing both approaches (Hybrid+SAS and MoL+SAS) across different architectural configurations. All experiments were Implemented in TensorFlow and trained on a Google Colab environment with a T4 GPU. We use the Adam optimizer with a learning rate of 0.001. For the hybrid algorithm, we initialize the threshold (Tinit) to 0.3 and adaptively adjust it during training. We discuss detailed hyperparameter settings in table \ref{tab:100k_movies}, table \ref{tab:1m_movies}

\newpage

\setlength{\tabcolsep}{1pt} % Increase column padding

\begin{table}[h]
	\centering
	\large
	\renewcommand{\arraystretch}{1.7} % Increase row spacing
	\resizebox{\textwidth}{!}{  % Scale table to fit width
		\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
			\hline
			\textbf{Model} & \textbf{\shortstack{Max \\ Sequence Length}} & 
			\textbf{\shortstack{Embedding \\ Dimension}} & 
			\textbf{\shortstack{Number \\ of Heads}} & 
			\textbf{\shortstack{Feedforward \\ Dimension}} & 
			\textbf{\shortstack{Batch \\ Size}} & 
			\textbf{Epochs} & 
			\textbf{\shortstack{Val \\ Loss}} & 
			\textbf{\shortstack{Val \\ Accuracy}} \\
			\hline
			Hybrid+SAS & 50  & 128  & 2 & 128  & 128 & 12 & 5.3036 & 0.1584  \\ \hline
			MoL+SAS    & 50  & 128  & 2 & 128  & 128 & 12 & 5.3152 & 0.1582  \\ \hline
			Hybrid+SAS & 128 & 256  & 4 & 256  & 128 & 10 & 3.6364 & 0.4301  \\ \hline
			MoL+SAS    & 128 & 256  & 4 & 256  & 128 & 10 & 3.6374 & 0.4299 \\\hline
			Hybrid+SAS & 512 & 512  & 4 & 512  & 128 & 10 & 1.2808 & 0.8120 \\ \hline
			MoL+SAS    & 512 & 512  & 4 & 512  & 128 & 10 & 1.3050 & 0.8016 \\\hline
		\end{tabular}
	}
	\caption{Results on 100kMovies dataset}
	\label{tab:100k_movies}
\end{table}
\setlength{\tabcolsep}{1pt} % Increase column padding
\begin{table}[h]
	\centering
	\large
	\renewcommand{\arraystretch}{1.7} % Increase row spacing
	\resizebox{\textwidth}{!}{  % Scale table to fit width
		\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
			\hline
			\textbf{Model} & \textbf{\shortstack{Max \\ Sequence Length}} & 
			\textbf{\shortstack{Embedding \\ Dimension}} & 
			\textbf{\shortstack{Number \\ of Heads}} & 
			\textbf{\shortstack{Feedforward \\ Dimension}} & 
			\textbf{\shortstack{Batch \\ Size}} & 
			\textbf{Epochs} & 
			\textbf{\shortstack{Val \\ Loss}} & 
			\textbf{\shortstack{Val \\ Accuracy}} \\
			\hline
			Hybrid+SAS & 50  & 128  & 2 & 128  & 128 & 10 & 4.5721 & 0.1530  \\ \hline
			MoL+SAS    & 50  & 128  & 2 & 128  & 128 & 10 & 4.5733 & 0.1526  \\ \hline
			Hybrid+SAS & 128 & 256  & 4 & 256  & 128 & 10 & 3.4152 & 0.3680  \\ \hline
			MoL+SAS    & 128 & 256  & 4 & 256  & 128 & 10 & 3.4671 & 0.3627  \\ \hline
			Hybrid+SAS & 512 & 512  & 4 & 512  & 128 & 10 & 1.0275 & 0.8350  \\ \hline
			MoL+SAS    & 512 & 512  & 4 & 512  & 128 & 10 & 1.0350 & 0.8276  \\ \hline

		\end{tabular}
	}
	\caption{Results on 1M Movies dataset}
	\label{tab:1m_movies}
\end{table}
Both approaches demonstrate significant performance improvements as model capacity increases, with larger configurations consistently delivering better results. For instance, when increasing the model's capacity such as expanding the (Max Sequence Length: 512, Embedding Dimension: 512, Number of Heads: 4, Feed-Forward Dimension: 512) the hybrid algorithm combined with SASRec (Hybrid+SAS) achieves notable gains, particularly in the most resource-intensive setup. On the ML-100K dataset, Hybrid+SAS reaches a score of\textbf{0.8120} compared to the baseline's \textbf{0.8016}, while on ML-1M, it achieves \textbf{0.8350} versus \textbf{0.8276} The ML-1M dataset generally benefits more from increased capacity, with the performance gap between datasets narrowing as the model scales. While smaller configurations provide a balance of efficiency and performance, the largest configuration, despite its higher computational demands, yields the best results, making it suitable for scenarios where resources are not a constraint. Both approaches show similar benefits from scaling, but Hybrid+SAS maintains a consistent edge in performance.

\subsection {Impact of Adaptive k-Variations on Model Performance}
As shown in Figures~\ref{fig:k_changes_100K} and \ref{fig:k_changes_1M}, the value of $k$ fluctuates across epochs for both MovieLens 100K and MovieLens 1M datasets. These variations indicate the adaptive nature of $k$ in response to the dataset characteristics and training progress. In the following section, we analyze how these changes influence model performance.

\begin{figure}[htbp]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Figures/CHAGES_OF_K_FOR_100k.png}
		\caption{K changes across epochs for MovieLens 100K}
		\label{fig:k_changes_100K}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Figures/chnages_inK_for_1M.png}
		\caption{K changes across epochs for MovieLens 1M}
		\label{fig:k_changes_1M}
	\end{subfigure}
	\caption{Comparison of K changes across epochs for different datasets}
	\label{fig:k_changes}
\end{figure}
the value of K changed dynamically during training, with different behaviors. For the MovieLens 100K dataset, K showed a steady increase across epochs, whereas for the MovieLens 1M dataset, K began at a lower value, experienced fluctuations, peaked, and then stabilized. This indicates that the larger dataset necessitated more adaptive adjustments in retrieval compared to the smaller dataset.\\
Figure~\ref{histo_p} summarizes the performance of our hybrid algorithm compared to the MoL-based approach on the MovieLens 100K and 1M datasets, both tested using a Max Sequence Length of 50, an Embedding Dimension of 128, 2 Attention Heads, a Feedforward Dimension of 128, a Batch Size of 128, and trained for 10 epochs . \\
\begin{figure}[ht]
	\centering
	\includegraphics[width=0.7\textwidth]{Figures/HISTOGRAM.png}
	\caption{Comparison of Models Across Evaluation Metrics}\label{histo_p}
\end{figure}
The variations in K help explain the performance differences seen in the fig \ref{histo_p}. The Hybrid+SAS model applied to the MovieLens 1M dataset, which exhibited more dynamic changes in K achieved higher HR@50(0.3631) and HR@200(0.6170) scores, reflecting better long-range recommendation quality. The fluctuations in K in the 1M dataset likely allowed the model to balance exploration and precision, improving its overall ranking performance.

On the other hand, the more gradual K increase in the 100K dataset resulted in relatively lower scores, suggesting that a static or overly conservative 
K selection might limit retrieval effectiveness.

Additionally, the MoL+SAS model achieved better performance than Hybrid+SAS in HR@10 for both datasets. This aligns with the observation that MoL+SAS tended to retrieve fewer but more relevant items at shorter ranking positions. This behavior can be attributed to how K evolved during training?smaller K values in earlier epochs likely enabled MoL+SAS to maintain higher precision at shorter ranks.
These findings highlight the importance of dynamically tuning K based on dataset characteristics to optimize recommendation effectiveness.

The results demonstrate that the Hybrid Exact Top-k algorithm effectively leverages both sequential user behavior and item metadata to improve recommendation quality. The adaptive MoL threshold allows the model to dynamically refine candidate items during training, leading to better performance. The improvements are consistent across both datasets, highlighting the robustness of our approach.\\
%%=============================================%%

\section{Conclusion}

The experimental results demonstrate the effectiveness of our proposed algorithm when applied to SASRec. Through extensive evaluation on the MovieLens-100K and MovieLens-1M datasets, we observe that our method consistently outperforms the baseline models, including SASRec with MOL. Our approach shows improvements in key evaluation metrics, particularly in Hit Rate (HR@k) and Normalized Discounted Cumulative Gain (NDCG@k), indicating better recommendation relevance. Furthermore, the results highlight the importance of hyperparameter tuning, as different configurations significantly impact model performance. 
Overall, the findings confirm that incorporating our algorithm enhances sequential recommendation capabilities, making it a promising approach for future research and real-world applications. Future work will focus on further optimizing the model and testing on additional datasets to validate its generalizability.

### 2025-04-15 Thesis/Latex/Dedication.tex

\thispagestyle{empty}
\begin{tikzpicture}[remember picture, overlay]
	\node at (current page){
		\includegraphics[width=\paperwidth,height=\paperheight]{Figures/bgg4.png}} ;
\end{tikzpicture}
\vskip15mm
\begin{center}
	\resizebox{6cm}{1.1cm}{\calligra Dedication} 
\end{center}
%

\thispagestyle{empty}

>>>>

\thispagestyle{empty}
\begin{tikzpicture}[remember picture, overlay]
	\node at (current page){
		\includegraphics[width=\paperwidth,height=\paperheight]{Figures/bgg4.png}} ;
\end{tikzpicture}
\vskip15mm
\begin{center}
	\resizebox{6cm}{1.1cm}{\calligra Dedication} 
\end{center}
\vfill 
\begin{center}
	\parbox{.85\linewidth}{\centering 
		\baselineskip=8mm 
		\fontfamily{pzc}\selectfont 
		\Large 
This work is dedicated with deep love and gratitude to:
\\[5mm]
My dear parents,
whose unwavering support, sacrifices, and constant prayers have been the foundation of everything I’ve achieved. Your belief in me gave me the strength to persevere through every challenge.
\\[5mm]
My supervisor, Mr. [Mr Salem Mohamed],
whose patient guidance, insightful feedback, and continuous encouragement made this journey not only possible but meaningful. Your dedication, expertise, and belief in my potential have left a lasting impact on me both academically and personally.
\\[5mm]
My beloved sister,
for being my greatest cheerleader and my constant source of emotional support. Your encouragement and care during the toughest moments meant the world to me.
\\[5mm]
My wonderful friend [nial hadjer],
for always being there with kind words, late-night conversations, and unshakable support.
\\[19mm]
}
\end{center}
\vfill 
\thispagestyle{empty}

### 2025-04-15 Thesis/Latex/Images_sources.tex

\begin{landscape}
	\thispagestyle{empty}
	\begin{center}
		\Huge{\textbf{Sources of Images}} \\
		\normalsize{\textit{for Copyright purposes}}
	\end{center}
	Figure 2.1 from \url{www.site1.com} \\
	Figure 2.3 from \url{www.site2.fr} \\
	Figure 2.5 from \url{www.site3.com} \\
	Figure 2.9 from \url{www.site4.com} \\
	Figure 3.5 from \url{www.site5.com} \\
	Figure 2.3 from \url{www.site2.fr} \\
	Figure 2.5 from \url{www.site3.com} \\
	Figure 2.9 from \url{www.site4.com} \\
	Figure 3.5 from \url{www.site5.com} \\
\end{landscape}

>>>>

\begin{landscape}
	\thispagestyle{empty}
	\begin{center}
		\Huge{\textbf{Sources of Images}} \\
		\normalsize{\textit{for Copyright purposes}}
	\end{center}
	Figure 1.1 from \url{https://blog.dataiku.com/nlp-metamorphosis} \\
	Figure 1.2 from \url{www.dmice.ohsu.edu/hersh/ohsu-pathology-20.pdf} \\
	Figure 1.3 from \url{https://w.wiki/3sAW} \\
	Figure 1.4 from \url{www.researchgate.net/publication/336092695_Densely_Connected_Convolutional_Networks_With_Attention_LSTM_for_Crowd_Flows_Prediction} \\
   Figure 1.5 from \href{https://www.medium.com/huggingface/encoder-decoders-in-transformers-a-hybrid-pre-trained-architecture-for-seq2seqaf4d7bf14bb8}{Medium article  transformers}\\
	Figure 1.6 from \href{https://medium.com/@anishnama20/exploring-the-power-of-encoder-decoder-models-pros-cons-and-applications-8bfbe2e66e76}{Medium article on encoder-decoders }	\\
	Figure 1.7 from \url{arxiv.org/abs/2307.09288} \\
	Figure 2.1 from \url{https://arxiv.org/abs/2312.10997} \\
	Figure 2.2 from \href{https://www.researchgate.net/figure/High-level-overview-of-a-possible-solution-using-RAG-and-a-multi-modal-in-context_fig1_380540048}{RAG } \\
   Figure 3.1 from \url{https://ai.gopubby.com/advanced-rag-techniques-unlocking-the-next-level-040c205b95bc} \\
	Figure 3.2 from \url{www.evidentlyai.com/ranking-metrics/precision-recall-at-k} \\
	Figure 3.3 from \url{www.evidentlyai.com/ranking-metrics/precision-recall-at-k} \\
	Figure 3.4 from \url{openreview.net/forum?id=eHF4pDRWjT} \\
	Figure 3.6 from \url{d2l.ai/chapter_recommender-systems/recsys-intro.html} \\
	Figure 3.7 from \url{arxiv.org/abs/1808.09781} \\
\end{landscape}
